Untitled

### 2019-05-03 R/model.Rmd
added set.seed

data07 <- filter(nla.cc, year == 2007, tmean_2m < 70) %>%
            dplyr::select(tmean_2m, date, longitude, latitude, tmean, tmean_dm1,
            tmean_avg3, tmean_avg7, tmean_avg30, percent_impervious, surface_area,
            shoreline_length, shoreline_dev, max_length, max_width, mean_width,
            max_depth, max_depth, volume, elevation)

data12 <- filter(nla.cc, year == 2012, tmean_2m < 70) %>%
            dplyr::select(tmean_2m, date, longitude, latitude, tmean, tmean_dm1,
            tmean_avg3, tmean_avg7, tmean_avg30, percent_impervious, surface_area,
            shoreline_length, shoreline_dev, max_length, max_width, mean_width,
            max_depth, max_depth, volume, elevation)

@@

##variable selection for 2007-only model
var_sel_tmean07 <- varsel_regression_rf(data07$tmean_2m, select(data07, -tmean_2m), ntree=1000, prog=TRUE, importance=TRUE)

varsel_plot(var_sel_tmean07)

var_sel_tmean07$vars[[9]]

##Variable selection for 2012-only model
var_sel_tmean12 <- varsel_regression_rf(data12$tmean_2m, select(data12, -tmean_2m),                ntree=1000, prog=TRUE,importance=TRUE)

varsel_plot(var_sel_tmean12) #9 variables

var_sel_tmean12$vars[[9]]

##Variable selection for 2007&2012 model
var_sel_tmean <- varsel_regression_rf(nla.all$tmean_2m, select(nla.all, -tmean_2m),                ntree=1000, prog=TRUE, importance=TRUE)

@@

RF2007 <- data07 %>%

  select(tmean_2m,var_sel_tmean07$vars[[9]]) %>%

RF2007

varImpPlot(RF2007)

RF2012 <- data12 %>%

  select(tmean_2m,var_sel_tmean12$vars[[9]]) %>%

RF2012

varImpPlot(RF2012)

RFAll <- nla.all %>%

>>>>

# data07 <- filter(nla.cc, year == 2007, tmean_2m < 70) %>%
#             dplyr::select(tmean_2m, date, longitude, latitude, tmean, tmean_dm1,
#             tmean_avg3, tmean_avg7, tmean_avg30, percent_impervious, surface_area,
#             shoreline_length, shoreline_dev, max_length, max_width, mean_width,
#             max_depth, max_depth, volume, elevation)
#             
#             
# data12 <- filter(nla.cc, year == 2012, tmean_2m < 70) %>%
#             dplyr::select(tmean_2m, date, longitude, latitude, tmean, tmean_dm1,
#             tmean_avg3, tmean_avg7, tmean_avg30, percent_impervious, surface_area,
#             shoreline_length, shoreline_dev, max_length, max_width, mean_width,
#             max_depth, max_depth, volume, elevation)

@@

##variable selection for 2007-only model
# var_sel_tmean07 <- varsel_regression_rf(data07$tmean_2m, select(data07, -tmean_2m), ntree=1000, prog=TRUE, importance=TRUE)
# 
# varsel_plot(var_sel_tmean07) 
# 
# var_sel_tmean07$vars[[9]]
# 
# 
# ##Variable selection for 2012-only model
# var_sel_tmean12 <- varsel_regression_rf(data12$tmean_2m, select(data12, -tmean_2m),                ntree=1000, prog=TRUE,importance=TRUE)
# 
# varsel_plot(var_sel_tmean12) #9 variables
# 
# var_sel_tmean12$vars[[9]]

##Variable selection for 2007&2012 model
set.seed(42)
var_sel_tmean <- varsel_regression_rf(nla.all$tmean_2m, select(nla.all, -tmean_2m),                ntree=1000, prog=TRUE, importance=TRUE)

@@

# RF2007 <- data07 %>%
# 
#   select(tmean_2m,var_sel_tmean07$vars[[9]]) %>%
# 
#   randomForest(tmean_2m ~ ., data = ., importance = TRUE, 
# 
#                ntree = 10000)
# 
# 
# 
# RF2007
# 
# varImpPlot(RF2007)
# 
# 
# 
# RF2012 <- data12 %>%
# 
#   select(tmean_2m,var_sel_tmean12$vars[[9]]) %>%
# 
#   randomForest(tmean_2m ~ ., data = ., importance = TRUE, 
# 
#                ntree = 10000)
# 
# 
# 
# RF2012
# 
# varImpPlot(RF2012)
#

set.seed(42)
RFAll <- nla.all %>%
